---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/ednstest.svg?branch=master)](https://travis-ci.org/hrbrmstr/ednstest) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/ednstest/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/ednstest)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ednstest)](https://cran.r-project.org/package=ednstest)

# ednstest

'RFC' 6891 ('EDNS') Compliance Checker

## Description

Checks 'Domain Name System' ('DNS') zones for compliance with  'RFC' 6891 ('EDNS').

You can read more about this at the [DNS Flag Day website](https://dnsflagday.net/), but the minimal working setup which will allow your domain to survive 2019 DNS flag day must not have `timeout` result in any of plain DNS and EDNS version 0 tests implemented in [ednscomp](https://ednscomp.isc.org/ednscomp) tool.

## What's Inside The Tin

The following functions are implemented:

- `ednstest`:	'RFC' 6891 ('EDNS') Compliance Checker

## Installation

```{r install-ex, eval=FALSE}
devtools::install_git("https://sr.ht.com/~hrbrmstr/ednstest.git")
# or
devtools::install_git("https://gitlab.com/hrbrmstr/ednstest.git")
# or (if you must)
devtools::install_github("hrbrmstr/ednstest")
```

## Usage

```{r lib-ex}
library(ednstest)

# current version
packageVersion("ednstest")

```

```{r give-it-a-go, cache=TRUE}
edns_test("rud.is")

edns_test("rstudio.com")

edns_test("r-project.org")
```

## ednstest Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
